\subsubsection{The phrase ``blessed is the man"}

The phrase ``blessed is the man'' is found 13 times in scripture:
\begin{compactenum}
    \item \textbf{Psalm 1:1} Blessed is the man that walketh not in the counsel of the ungodly, nor standeth in the way of sinners, nor sitteth in the seat of the scornful.
    \item \textbf{Psalm 32:2} Blessed is the man unto whom the LORD imputeth not iniquity, and in whose spirit there is no guile
    \item \textbf{Psalm 34:8} O taste and see that the LORD is good: blessed is the man that trusteth in him.
    \item \textbf{Psalm 65:4} Blessed is the man whom thou choosest, and causest to approach unto thee, that he may dwell in thy courts: we shall be satisfied with the goodness of thy house, even of thy holy temple.
    \item \textbf{Psalm 84:5}  Blessed is the man whose strength is in thee; in whose heart are the ways of them.
    \item \textbf{Psalm 84:12} O LORD of hosts, blessed is the man that trusteth in thee.
    \item \textbf{Psalm 94:12} Blessed is the man whom thou chastenest, O LORD, and teachest him out of thy law
    \item \textbf{Psalm 112:1} Praise ye the LORD. Blessed is the man that feareth the LORD, that delighteth greatly in his commandments
    \item \textbf{Proverb 8:34} Blessed is the man that heareth me, watching daily at my gates, waiting at the posts of my doors.
    \item \textbf{Isaiah  56:1-2} Thus saith the LORD, Keep ye judgment, and do justice: for my salvation is near to come, and my righteousness to be revealed. [2] Blessed is the man that doeth this, and the son of man that layeth hold on it; that keepeth the sabbath from polluting it, and keepeth his hand from doing any evil.
    \item \textbf{Jeremiah 17:7} Blessed is the man that trusteth in the LORD, and whose hope the LORD is.
    \item \textbf{Romans 4:8} Blessed is the man to whom the Lord will not impute sin.
    \item \textbf{James 1:12} Blessed is the man that endureth temptation: for when he is tried, he shall receive the crown of life, which the Lord hath promised to them that love him.\\
\end{compactenum}

\noindent So, then, there is a connection between man and a rebellion against being blessed by God. The Biblical interpretation principle ``The Law of First Mention'' for this phrase is seen in Psalm 1:1 which tells rebellious mankind how to be blessed. The last occurrence in James 1:12 is a bookend on the principle - a man will be blessed by enduring temptation.
