\subsubsection{The phrase ``whole heart"}

The phrase ``whole heart'' is found 13 times in scripture, 7 times in Psalm 119:
\begin{compactenum}
    \item Psalm 9:1 I will praise thee, O LORD, with my whole heart; I will shew forth all thy marvellous works.
    \item Psalm 111:1 Praise ye the LORD. I will praise the LORD with my whole heart, in the assembly of the upright, and in the congregation.
    \item Psalm 119:2 Blessed are they that keep his testimonies, and that seek him with the whole heart.
    \item Psalm 119:10 With my whole heart have I sought thee: O let me not wander from thy commandments.
    \item Psalm 119:34 Give me understanding, and I shall keep thy law; yea, I shall observe it with my whole heart.
    \item Psalm 119:58  I intreated thy favour with my whole heart: be merciful unto me according to thy word.
    \item Psalm 119:69 The proud have forged a lie against me: but I will keep thy precepts with my whole heart.
    \item Psalm 119:145 I cried with my whole heart; hear me, O LORD: I will keep thy statutes.
    \item Psalm 138:1 I will praise thee with my whole heart: before the gods will I sing praise unto thee.
    \item Isaiah 1:5 Why should ye be stricken any more? ye will revolt more and more: the whole head is sick, and the whole heart faint.
    \item Jeremiah 3:10 And yet for all this her treacherous sister Judah hath not turned unto me with her whole heart, but feignedly, saith the LORD.
    \item Jeremiah 24:7 And I will give them an heart to know me, that I am the LORD: and they shall be my people, and I will be their God: for they shall return unto me with their whole heart.
    \item Jeremiah 32:41 Yea, I will rejoice over them to do them good, and I will plant them in this land assuredly with my whole heart and with my whole soul.
\end{compactenum}