\subsubsection{The phrase ``between the cherubims"}

The phrase ``between the cherubims'' is found 11 times in scripture:
\begin{compactenum}
    \item \textbf{1 Samuel 4:4} So the people sent to Shiloh, that they might bring from thence the ark of the covenant of the LORD of hosts, which dwelleth between the cherubims: and the two sons of Eli, Hophni and Phinehas, were there with the ark of the covenant of God.
    \item \textbf{2 Samuel 6:2} And David arose, and went with all the people that were with him from Baale of Judah, to bring up from thence the ark of God, whose name is called by the name of the LORD of hosts that dwelleth between the cherubims.
    \item \textbf{2 Kings 19:15} And Hezekiah prayed before the LORD, and said, O LORD God of Israel, which dwellest between the cherubims, thou art the God, even thou alone, of all the kingdoms of the earth; thou hast made heaven and earth.
    \item \textbf{1 Chronicles 13:6} And David went up, and all Israel, to Baalah, that is, to Kirjath–jearim, which belonged to Judah, to bring up thence the ark of God the LORD, that dwelleth between the cherubims, whose name is called on it.
    \item \textbf{Psalm 80:1} Give ear, O Shepherd of Israel, thou that leadest Joseph like a flock; thou that dwellest between the cherubims, shine forth.
    \item \textbf{Psalm 99:1} The LORD reigneth; let the people tremble: he sitteth between the cherubims; let the earth be moved.
    \item \textbf{Isaiah 37:16} O LORD of hosts, God of Israel, that dwellest between the cherubims, thou art the God, even thou alone, of all the kingdoms of the earth: thou hast made heaven and earth.
    \item \textbf{Ezekiel 10:2, 6, 7} (4x) And he spake unto the man clothed with linen, and said, Go in between the wheels, even under the cherub, and fill thine hand with coals of fire from between the cherubims, and scatter them over the city. And he went in in my sight. [6] And it came to pass, that when he had commanded the man clothed with linen, saying, Take fire from between the wheels, from between the cherubims; then he went in, and stood beside the wheels. [7] And one cherub stretched forth his hand from between the cherubims unto the fire that was between the cherubims, and took thereof, and put it into the hands of him that was clothed with linen: who took it, and went out.
\end{compactenum}