\subsubsection{The phrase ``all the day long"}

The  phrase ``all the day long'' is found 13 times in scripture: Deut 28:32, 33:12, Ps 32;3, 35:28, 38:6, 28:12, 44:8, 44:22, 71:24, 73:14, Pro 21:26, 23:17, and Romans 8:36.

\begin{compactenum}
    \item Deuteronomy 28:32 is part of the description of what will happen if Israel forsakes  her God. \footnote{\textbf{Deuteronomy 28:32} - Thy sons and thy daughters shall be given unto another people, and thine eyes shall look, and fail with longing for them all the day long: and there shall be no might in thine hand.}
    \item Deuteronomy 33:12 is a promise to the tribe of Benjamin. \footnote{\textbf{Deuteronomy 33:12} - And of Benjamin he said, The beloved of the LORD shall dwell in safety by him; and the LORD shall cover him all the day long, and he shall dwell between his shoulders.}
    \item Psalm 32:3 is in a Tribulation context with the silent grief and suffering being connected with drying of the bones.\footnote{\textbf{Psalm 32:3} - When I kept silence, my bones waxed old through my roaring all the day long.}
    \item Psalm 35:28 speaks of the persecuted one still choosing to praise God.\footnote{\textbf{Psalm 35:28} - And my tongue shall speak of thy righteousness and of thy praise all the day long.}
    \item Psalm 38:6 speaks of the persecuted one still choosing to praise God.\footnote{\textbf{Psalm 38:6} - I am troubled; I am bowed down greatly; I go mourning all the day long.}
    \item Psalm 38:12 speaks of the ones doing the persecuting.\footnote{\textbf{Psalm 38:12} - They also that seek after my life lay snares for me: and they that seek my hurt speak mischievous things, and imagine deceits all the day long.}
    \item Psalm 44:8 speaks of boasting of God all the day long.\footnote{\textbf{Psalm 44:8} - In God we boast all the day long, and praise thy name for ever. Selah.}
    \item But in Psalm 44:22, these people are killed all the day long.\footnote{\textbf{Psalm 44:22} - Yea, for thy sake are we killed all the day long; we are counted as sheep for the slaughter.}
    \item In Psalm 71:24, God's righteousness is being spoken of.\footnote{\textbf{Psalm 71:24} - My tongue also shall talk of thy righteousness all the day long: for they are confounded, for they are brought unto shame, that seek my hurt.}
    \item Psalm 73:14 speaks of the plagues and chastisement which happen all the day long.\footnote{\textbf{PSalm 73:14} - For all the day long have I been plagued, and chastened every morning.}
    \item The scorner in Proverb 21:26 covets all the day long.\footnote{\textbf{Proverb 21:26} -He coveteth greedily all the day long: but the righteous giveth and spareth not.}
    \item Proverb 23:17 tells us not to envy sinners, but to be in the fear of the Lord all the day long.\footnote{\textbf{Proverb 23:17} - Let not thine heart envy sinners: but be thou in the fear of the LORD all the day long.}
    \item Romans 8:36 quotes Psalm 44:22.\footnote{\textbf{Romans 8:36} - As it is written, For thy sake we are killed all the day long; we are accounted as sheep for the slaughter.}
\end{compactenum}