\subsubsection{Meddle, meddling,  meddleth, intermeddle and intermeddleth}

Forms of the word ``meddle'' are used 12 times in the King James, only in the Old Testament.  For the most part, meddling with things is spoken against. The general rule is to let God take care of the problem.

\begin{compactenum}[1.][10]
	\item  \textbf{Deuteronomy 2:5} \fcolorbox{bone}{bone}{Meddle} not with them; for I will not give you of their land, no, not so much as a foot breadth; because I have given mount Seir unto Esau for a possession.
	\item \textbf{Deuteronomy 2:19} And when thou comest nigh over against the children of Ammon, distress them not, nor \fcolorbox{bone}{bone}{meddle} with them: for I will not give thee of the land of the children of Ammon any possession; because I have given it unto the children of Lot for a possession.
	\item \textbf{2 Kings 14:10} Thou hast indeed smitten Edom, and thine heart hath lifted thee up: glory of this, and tarry at home: for why shouldest thou \fcolorbox{bone}{bone}{meddle} to thy hurt, that thou shouldest fall, even thou, and Judah with thee?
	\item \textbf{2 Chronicles 25:19} Thou sayest, Lo, thou hast smitten the Edomites; and thine heart lifteth thee up to boast: abide now at home; why shouldest thou \fcolorbox{bone}{bone}{meddle} to thine hurt, that thou shouldest fall, even thou, and Judah with thee?
	\item \textbf{2 Chronicles 35:21} But he sent ambassadors to him, saying, What have I to do with thee, thou king of Judah? I come not against thee this day, but against the house wherewith I have war: for God commanded me to make haste: forbear thee from \fcolorbox{bone}{bone}{meddling} with God, who is with me, that he destroy thee not.
	\item \textbf{Proverb 14:10} The heart knoweth his own bitterness; and a stranger doth not \fcolorbox{bone}{bone}{intermeddle} with his joy.
	\item \textbf{Proverb 17:14} The beginning of strife is as when one letteth out water: therefore leave off contention, before it be \fcolorbox{bone}{bone}{meddled} with.
	\item \textbf{Proverb 18:1} Through desire a man, having separated himself, seeketh and \fcolorbox{bone}{bone}{intermeddleth} with all wisdom.
	\item \textbf{Proverb 20:3} It is an honour for a man to cease from strife: but every fool will be \fcolorbox{bone}{bone}{meddling}.
	\item \textbf{Proverb 20:19} He that goeth about as a talebearer revealeth secrets: therefore \fcolorbox{bone}{bone}{meddle} not with him that flattereth with his lips.
	\item \textbf{Proverb 24:21} My son, fear thou the LORD and the king: and \fcolorbox{bone}{bone}{meddle} not with them that are given to change:
	\item \textbf{Proverb 26:17} He that passeth by, and \fcolorbox{bone}{bone}{meddleth} with strife belonging not to him, is like one that taketh a dog by the ears.
\end{compactenum}
