\subsubsection{Forms of the word ``brute"}
There are 13 occurrences of forms of the word ``brute'' in scripture. So, the word should be considered along with other words in the club of those found 13 times.

\begin{compactenum}
    \item \textbf{Psalm 49:10} For he seeth that wise men die, likewise the fool and the brutish person perish, and leave their wealth to others. (``brutish'' is the 13th word)
    \item \textbf{Psalm 92:6}  A brutish man knoweth not; neither doth a fool understand this.
    \item \textbf{Psalm 94:8} Understand, ye brutish among the people: and ye fools, when will ye be wise?
    \item \textbf{Proverb 12:1}  Whoso loveth instruction loveth knowledge: but he that hateth reproof is brutish.
    \item \textbf{Proverb 30:2} Surely I am more brutish than any man, and have not the understanding of a man.
    \item \textbf{Isaiah 19:11} Surely the princes of Zoan are fools, the counsel of the wise counsellors of Pharaoh is become brutish: how say ye unto Pharaoh, I am the son of the wise, the son of ancient kings?
    \item \textbf{Jeremiah 10:8} But they are altogether brutish and foolish: the stock is a doctrine of vanities.
    \item \textbf{Jeremiah 10:14} Every man is brutish in his knowledge: every founder is confounded by the graven image: for his molten image is falsehood, and there is no breath in them.
    \item \textbf{Jeremiah 10:21}  For the pastors are become brutish, and have not sought the LORD: therefore they shall not prosper, and all their flocks shall be scattered.
    \item \textbf{Jeremiah 51:17} Every man is brutish by his knowledge; every founder is confounded by the graven image: for his molten image is falsehood, and there is no breath in them.
    \item \textbf{Ezekiel 21:31} And I will pour out mine indignation upon thee, I will blow against thee in the fire of my wrath, and deliver thee into the hand of brutish men, and skilful to destroy.
    \item \textbf{2 Peter 2:12} But these, as natural brute beasts, made to be taken and destroyed, speak evil of the things that they understand not; and shall utterly perish in their own corruption;
    \item \textbf{Jude 1:10} But these speak evil of those things which they know not: but what they know naturally, as brute beasts, in those things they corrupt themselves.
\end{compactenum}