\subsubsection{The phrase ``the ungodly"}

The phrase ``the ungodly,'' is found 13 times in scripture.

\begin{compactenum}
    \item 2 Chronicles 19:2 - And Jehu the son of Hanani the seer went out to meet him, and said to king Jehoshaphat, Shouldest thou help the ungodly, and love them that hate the LORD? therefore is wrath upon thee from before the LORD.
    \item Job 16:11 -  God hath delivered me to the ungodly, and turned me over into the hands of the wicked.
    \item Psalm 1:1 - Blessed is the man that walketh not in the counsel of the ungodly, nor standeth in the way of sinners, nor sitteth in the seat of the scornful.
    \item Psalm 1:4 - The ungodly are not so: but are like the chaff which the wind driveth away.
    \item Psalm 1:5 - Therefore the ungodly shall not stand in the judgment, nor sinners in the congregation of the righteous.
    \item Psalm 1:6 - For the LORD knoweth the way of the righteous: but the way of the ungodly shall perish.
    \item Psalm 3:7 - Arise, O LORD; save me, O my God: for thou hast smitten all mine enemies upon the cheek bone; thou hast broken the teeth of the ungodly.
    \item Psalm 73:12 - Behold, these are the ungodly, who prosper in the world; they increase in riches.
    \item Romans 4:5 - But to him that worketh not, but believeth on him that justifieth the ungodly, his faith is counted for righteousness.
    \item Romans 5:6 - For when we were yet without strength, in due time Christ died for the ungodly.
    \item 1 Timothy 1:9 - Knowing this, that the law is not made for a righteous man, but for the lawless and disobedient, for the ungodly and for sinners, for unholy and profane, for murderers of fathers and murderers of mothers, for manslayers,
    \item 1 Peter 4:18 - And if the righteous scarcely be saved, where shall the ungodly and the sinner appear?
    \item 2 Peter 2:5 - And spared not the old world, but saved Noah the eighth person, a preacher of righteousness, bringing in the flood upon the world of the ungodly;
\end{compactenum}