\chapter{Leviticus 9}
\marginpar{\scriptsize \centering \fcolorbox{bone}{lime}{\textbf{A NEW PRIEST}}\\ (Levitcus 9:1--24) 
\begin{compactenum}[I.][8]
     \item \textbf{Goat Appointed} as the sin offering \index[scripture]{Leviticus!Lev 09:03}\index[scripture]{Leviticus!Lev 09:15}(Lev 9:3, 15)
    \item The \textbf{Gathering for the Affair} \index[scripture]{Leviticus!Lev 09:05}(Lev 9:5)
    \item \textbf{Going to the Altar} \index[scripture]{Leviticus!Lev 09:06}(Lev 9:6)
    \item \textbf{Gift Allotted} \index[scripture]{Leviticus!Lev 09:18}(Lev 9:18)
     \item \textbf{Greeting \& Grace Applied} \index[scripture]{Leviticus!Lev 09:22}(Lev 9:22)
   \item The \textbf{Glory} that Appeared \index[scripture]{Leviticus!Lev 09:23}(Lev 9:23)
\end{compactenum} }







\footnote{\textcolor[cmyk]{0.99998,1,0,0}{\hyperlink{TOC}{Return to end of Table of Contents.}}}\footnote{\href{https://audiobible.com/bible/leviticus_9.html}{\textcolor[cmyk]{0.99998,1,0,0}{Leviticus 9 Audio}}}\textcolor[cmyk]{0.99998,1,0,0}{And it came to pass on the eighth day, \emph{that} Moses called Aaron and his sons, and the elders of Israel;}
[2] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{he} said unto Aaron, Take thee a young calf  \fcolorbox{bone}{bone}{he} a sin offering, and a ram  \fcolorbox{bone}{bone}{he} a burnt offering, without blemish, and offer \emph{them} before the LORD.}
[3] \textcolor[cmyk]{0.99998,1,0,0}{And unto the children of Israel thou shalt speak, saying, Take ye a kid of the \fcolorbox{bone}{lime}{goats}  \fcolorbox{bone}{bone}{he} a sin offering; and a calf and a lamb, \emph{both} of the first year, without blemish,  \fcolorbox{bone}{bone}{he} a burnt offering;}
[4] \textcolor[cmyk]{0.99998,1,0,0}{Also a bullock and a ram  \fcolorbox{bone}{bone}{he} peace offerings, to sacrifice before the LORD; and a meat offering mingled with oil:  \fcolorbox{bone}{bone}{he} to day the LORD will appear unto you.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And they brought \emph{that} which Moses commanded before the tabernacle of the congregation: and all the \fcolorbox{bone}{lime}{congregation} drew near and stood before the LORD.}
[6] \textcolor[cmyk]{0.99998,1,0,0}{And Moses said, This \emph{is} the thing which the LORD \fcolorbox{bone}{lime}{commanded} that ye should do: and the glory of the LORD shall appear unto you.}
[7] \textcolor[cmyk]{0.99998,1,0,0}{And Moses said unto Aaron, Go unto the altar, and offer thy sin offering, and thy burnt offering, and make an atonement  \fcolorbox{bone}{bone}{he} thyself, and  \fcolorbox{bone}{bone}{he} the people: and offer the offering of the people, and make an atonement  \fcolorbox{bone}{bone}{he} them; as the LORD commanded.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{Aaron therefore went unto the altar, and slew the calf of the sin offering, which \emph{was}  \fcolorbox{bone}{bone}{he} himself.}
[9] \textcolor[cmyk]{0.99998,1,0,0}{And the sons of Aaron brought the blood unto him: and \fcolorbox{bone}{bone}{he} dipped his finger in the blood, and put \emph{it} upon the horns of the altar, and poured out the blood at the bottom of the altar:}
[10] \textcolor[cmyk]{0.99998,1,0,0}{But the fat, and the kidneys, and the caul above the liver of the sin offering, \fcolorbox{bone}{bone}{he} burnt upon the altar; as the LORD commanded Moses.}
[11] \textcolor[cmyk]{0.99998,1,0,0}{And the flesh and the hide \fcolorbox{bone}{bone}{he} burnt with fire without the camp.}
[12] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{he} slew the burnt offering; and Aaron's sons presented unto him the blood, which \fcolorbox{bone}{bone}{he} sprinkled round about upon the altar.}
[13] \textcolor[cmyk]{0.99998,1,0,0}{And they presented the burnt offering unto him, with the pieces thereof, and the head: and \fcolorbox{bone}{bone}{he} burnt \emph{them} upon the altar.}
[14] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{he} did wash the inwards and the legs, and burnt \emph{them} upon the burnt offering on the altar.}\\
\\
\P \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{he} brought the people's offering, and took the \fcolorbox{bone}{lime}{goat}, which \emph{was} the sin offering  \fcolorbox{bone}{bone}{he} the people, and slew it, and offered it  \fcolorbox{bone}{bone}{he} sin, as the first.}
[16] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{he} brought the burnt offering, and offered it according to the manner.}
[17] \textcolor[cmyk]{0.99998,1,0,0}{And \fcolorbox{bone}{bone}{he} brought the meat offering, and took an handful thereof, and burnt \emph{it} upon the altar, beside the burnt sacrifice of the morning.}
[18] \textcolor[cmyk]{0.99998,1,0,0}{He slew also the bullock and the ram \emph{for} \fcolorbox{bone}{lime}{a sacrifice} of peace offerings, which \emph{was}  \fcolorbox{bone}{bone}{he} the people: and Aaron's sons presented unto him the blood, which \fcolorbox{bone}{bone}{he} sprinkled upon the altar round about,}
[19] \textcolor[cmyk]{0.99998,1,0,0}{And the fat of the bullock and of the ram, the rump, and that which covereth \emph{the} \emph{inwards}, and the kidneys, and the caul \emph{above} the liver:}
[20] \textcolor[cmyk]{0.99998,1,0,0}{And they put the fat upon the breasts, and \fcolorbox{bone}{bone}{he} burnt the fat upon the altar:}
[21] \textcolor[cmyk]{0.99998,1,0,0}{And the breasts and the right shoulder Aaron waved \emph{for} a wave offering before the LORD; as Moses commanded.}
[22] \textcolor[cmyk]{0.99998,1,0,0}{And Aaron lifted up his hand toward the people, and blessed them, and came down from \fcolorbox{bone}{lime}{offering} of the sin offering, and the burnt offering, and peace offerings.}
[23] \textcolor[cmyk]{0.99998,1,0,0}{And Moses and Aaron went into the tabernacle of the congregation, and came out, and blessed the people: and the \fcolorbox{bone}{lime}{glory} of the LORD appeared unto all the people.}
[24] \textcolor[cmyk]{0.99998,1,0,0}{And there came a fire out from before the LORD, and consumed upon the altar the burnt offering and the fat: \emph{which} when all the people saw, they shouted, and fell on their faces.}